GPU-Accelerated Parallelization of Edge-Based Motion Detection Algorithms with the NVIDIA CUDA Framework

### 2015-12-01 documents/paper/paper.tex
Add FFT images

\subsection{Noise Elimination: Two-Dimensional Gaussian Filtering}
The first task in our edge detection algorithm is denoising the input in order to reduce the amount of high-frequency content in the image by as much as possible without destroying critical information points in the image (e.g. the real edges). We filter out high-frequency noise so that random noise is not mistakenly interpreted as an edge, as edges correspond to points in the image where the gradient has an above-threshold magnitude. \par
For example, consider the $5312$ x $2988$ pixel image (taken at a high ISO to deliberately introduce noise) of Figure \ref{noisy-image} and a plot of its grayscale intensity versus the image's spatial dimensions in Figure \ref{noisy-image-mesh}. It is clear from the mesh that there is much high-frequency noise, which can be removed with a low-pass filter.
\begin{figure}[H]
	\centering
	\includegraphics[width=0.45\textwidth]{noisy_image.jpg}
	\caption{Unfiltered noisy image}
    \label{noisy-image}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{noisy_image_mesh.jpg}
	\caption{Grayscale intensity of unfiltered noisy image at each pixel}
    \label{noisy-image-mesh}
\end{figure}
To low-pass filter our image, we apply a discrete Gaussian filter. Generally, a Gaussian blur kernel of size $2n + 1$ x $2n + 1$ ($\forall n \in \mathbb{Z}^+$, and with parameter $\sigma$) is given by
$$h[i, j] = \frac{1}{2\pi \sigma^2}e^{-\frac{(i - k - 1)^2 + (j - k - 1)^2}{2\sigma^2}}$$
Our implementation of Gaussian filtering uses the constant-sized ($k = 3$), constant-$\sigma$ kernel
\[
h[i, j] = \frac{1}{16}
\begin{bmatrix}
	1 & 2 & 1 \\
	2 & 4 & 2 \\
	1 & 2 & 1
\end{bmatrix}
\]
This kernel is implemented separably as
\[
h[i, j] = \frac{1}{16}
\begin{bmatrix}
	1 & 2 & 1
\end{bmatrix}
*
\begin{bmatrix}
	1 \\ 2 \\ 1
\end{bmatrix}
\] \par
Applying a Gaussian filter with parameters $k = 5$ and $\sigma = 5$ to the above image significantly denoises the image without sacrificing edge precision, which can be seen from the spatial intensity plot in Figure \ref{filtered-noisy-image-mesh}.
\begin{figure}[H]
	\centering
	\includegraphics[width=0.45\textwidth]{filtered_noisy_image.jpg}
	\caption{Gaussian-filtered noisy image with parameters $k = 3$ and $\sigma = 5$}
    \label{filtered-noisy-image}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{filtered_noisy_image_mesh.jpg}
	\caption{Grayscale intensity of Gaussian-filtered noisy image at each pixel}
    \label{filtered-noisy-image-mesh}
\end{figure}

@@

	\KwIn{Thresholded difference matrix $\boldsymbol{D}$, motion threshold $\Gamma$, width of the original image $M$, height of the original image $N$, number of horizontal divisions $m$, and number of vertical divisions $n$ ($m$ and $n$ are the dimensions of $\boldsymbol{D}'$)}
	\KwOut{The difference density matrix $\boldsymbol{D}'$ of dimensions $m$ x $n$ whose value is 1 if there is motion in that region, and 0 otherwise}

	\nl Initialize $\boldsymbol{D}'$ to 0 $\forall i \in [0, m - 1], \forall j \in [0, n - 1]$\;
	\nl \ForEach {$i \in [0, m - 1]$} {
		\nl \ForEach {$j \in [0, n - 1]$} {
			\nl $x \gets 0$\tcp*{Number of differences in this region}\
			\nl \ForEach{$i' \in [0, \frac{M}{n}]$} {
				\nl \ForEach{$j' \in [0, \frac{N}{n}]$} {
					\nl \If {$\boldsymbol{D}_{i + i', j + j'} \neq 0$} {
						\nl $x \gets x + 1$\;
					}
				}
			}
			\nl \If{$\frac{mn}{MN}x > \Gamma$} {
				\nl $\boldsymbol{D}'_{i, j} \gets 1$\;
			}
		}
	}
	\nl \Return $\boldsymbol{D}'$\;
	\
\end{algorithm}

@@

\section*{Acknowledgment}
Placeholder text

>>>>

\subsection{Noise Elimination: Two-Dimensional Gaussian Filtering}
The first task in our edge detection algorithm is denoising the input in order to reduce the amount of high-frequency content in the image by as much as possible without destroying critical information points in the image (e.g. the real edges). We filter out high-frequency noise so that random noise is not mistakenly interpreted as an edge, as edges correspond to points in the image where the gradient has an above-threshold magnitude. \par
For example, consider the $5312$ x $2988$ pixel image (taken at a high ISO to deliberately introduce noise) of Figure \ref{noisy-image} and a plot of its grayscale intensity versus the image's spatial dimensions in Figure \ref{noisy-image-mesh}. It is clear from the mesh that there is much high-frequency noise, which can be removed with a low-pass filter.
\begin{figure}[H]
	\centering
	\includegraphics[width=0.45\textwidth]{noisy_image.jpg}
	\caption{Unfiltered noisy image}
    \label{noisy-image}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{noisy_image_mesh.jpg}
	\caption{Grayscale intensity of unfiltered noisy image at each pixel}
    \label{noisy-image-mesh}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{fft_noisy_image.jpg}
	\caption{FFT magnitude of unfiltered noisy image at each pixel (log scale)}
    \label{noisy-image-fft}
\end{figure}
To low-pass filter our image, we apply a discrete Gaussian filter. Generally, a Gaussian blur kernel of size $2n + 1$ x $2n + 1$ ($\forall n \in \mathbb{Z}^+$, and with parameter $\sigma$) is given by
$$h[i, j] = \frac{1}{2\pi \sigma^2}e^{-\frac{(i - k - 1)^2 + (j - k - 1)^2}{2\sigma^2}}$$
Our implementation of Gaussian filtering uses the constant-sized ($k = 3$), constant-$\sigma$ kernel
\[
h[i, j] = \frac{1}{16}
\begin{bmatrix}
	1 & 2 & 1 \\
	2 & 4 & 2 \\
	1 & 2 & 1
\end{bmatrix}
\]
This kernel is implemented separably as
\[
h[i, j] = \frac{1}{16}
\begin{bmatrix}
	1 & 2 & 1
\end{bmatrix}
*
\begin{bmatrix}
	1 \\ 2 \\ 1
\end{bmatrix}
\] \par
Applying a Gaussian filter with parameters $k = 5$ and $\sigma = 5$ to the above image significantly denoises the image without sacrificing edge precision, which can be seen from the spatial intensity plot in Figure \ref{filtered-noisy-image-mesh}.
\begin{figure}[H]
	\centering
	\includegraphics[width=0.45\textwidth]{filtered_noisy_image.jpg}
	\caption{Gaussian-filtered noisy image with parameters $k = 3$ and $\sigma = 5$}
    \label{filtered-noisy-image}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{filtered_noisy_image_mesh.jpg}
	\caption{Grayscale intensity of Gaussian-filtered noisy image at each pixel}
    \label{filtered-noisy-image-mesh}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{fft_filtered_noisy_image.jpg}
	\caption{FFT magnitude of Gaussian-filtered noisy image at each pixel (log scale)}
    \label{filtered-noisy-image-fft}
\end{figure}

@@

	\KwIn{Thresholded difference matrix $\boldsymbol{D}$, motion threshold $\Gamma$, width of the original image $M$, height of the original image $N$, number of horizontal divisions $m$, and number of vertical divisions $n$}
	\KwOut{The difference density matrix $\boldsymbol{D}'$ of dimensions $m$ x $n$ whose value is 1 if there is motion in that region, and 0 otherwise}

	\nl Initialize $\boldsymbol{D}'$ to 0 $\forall i \in [0, m - 1], \forall j \in [0, n - 1]$\;
	\nl \ForEach {$i \in [0, m - 1]$} {
		\nl \ForEach {$j \in [0, n - 1]$} {
			\nl $x \gets 0$\tcp*{Number of differences in this region}
			\nl \ForEach{$i' \in [0, \frac{M}{n}]$} {
				\nl \ForEach{$j' \in [0, \frac{N}{n}]$} {
					\nl \If {$\boldsymbol{D}_{i + i', j + j'} \neq 0$} {
						\nl $x \gets x + 1$\;
					}
				}
			}
			\nl \If{$\frac{mn}{MN}x > \Gamma$} {
				\nl $\boldsymbol{D}'_{i, j} \gets 1$\;
			}
		}
	}
	\nl \Return $\boldsymbol{D}'$\;
	\
\end{algorithm}

@@

\section*{Acknowledgments}
Placeholder text
